Library of Actions: Implementing a Generic Robot Execution Framework by Using Manipulation Action Semantics

### 2015-01-05 paper_new.tex
soa updated

\title{Library of Actions: Implementing Human-like Manipulation Actions based on Semantic Event Chains}

@@

In this paper a new implementation of the library of actions is presented.
Library of actions is a software application which implements  manipulation actions on robotic systems using the semantic event chain framework.
A general definition for manipulation actions is presented which contains both in symbolic and sub-symbolic components.
To connect these two domains, a finite state machine is presented to execute manipulation actions.
The actions are performed both individually and chained sequentially to perform more complex scenarios.
This opens the possibility to use higher-level planners that work in symbolic domain.
The results show that the proposed methodology and software are capable of performing useful human-like actions.

@@

The rest of the paper is organized as follows. We start with introducing the state of the art. We then continue with a detailed description of each processing step. Next, we provide experimental results on various datasets and finally we finish with a discussion.

The rest of the paper is organized as follows.
The high-level action definition is presented in section.\ref{sec:high-level}.
The components of actions in the low-level are introduced in Section.\ref{sec:low-level}.
Section.\ref{sec:Implementing} presents the implementation of actions in the library.
The results of the experiments are shown in Section.\ref{sec:results} followed by some conclusions in Section.\ref{sec:conclusion}.

%\newpage  %% needed for single columns
%\clearpage  %% needed for two columns
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{State of the Art}
\label{sec:soa}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Segmentation and Tracking}
\label{sec:segmentationandtracking}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Semantic Event Chain (SEC) Extraction}
\label{sec:secs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Learning of Model SECs}
\label{sec:learning}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{High-level Action Definition}
\label{sec:high-level}
In this section we give a high-level definition of manipulation actions.
At this level, definitions are mainly symbolic, abstract and close to human description.

A simple action like putting a bucket on a box may be described by a human as following:
\begin{enumerate}
  \item \textbf{\textit{Approach}} the bucket
  \item \textbf{\textit{Grasp}} the bucket
  \item \textbf{\textit{Put}} the bucket on the box
  \item \textbf{\textit{Release}} the bucket
\end{enumerate}
This description is by no means unique.
One could easily describe the same action in different words, with different number of steps and different details.
However, one could still extract some properties from this simple description:
\begin{itemize}
  \item \textbf{Property 1:} The definition is valid even if the objects are changed.
  \item \textbf{Property 2:} An action can be broken into a sequence of smaller sub-actions such as \textit{approach} and \textit{grasp}.
  \item \textbf{Property 3:} There are conditions to end one sub-action and start the next. In the above example these conditions are rather implicit.
  \item \textbf{Property 4:} As humans, we roughly know how to perform these sub-actions.
  Although, our exact movements are produced when we see the objects and perform the action.
\end{itemize}

Our approach to execute human-like actions with robots is similar to this simple example.
We will define a high-level definition of actions which does not depend on the specific objects used in the action (Property 1),
and consists of a sequence of sub-actions (Property 2).
The conditions to start and end each sub-action are defined explicitly (Property 3).
We will store the default trajectory parameters to execute actions in the high-level definition.
When the real objects are seen at each specific instance of the action, these parameters are used to generate the movements (Property 4).

This high-level symbolic definition has several components which will be described in the rest of this section.
For the put-on-top example, the resulting components are shown in fig.\ref{fig:action_graph_sec}.
This definition is an extension to our previous works on the ontology of actions \cite{TAMD13}, semantic event chains (SEC) \cite{Aksoy11b},
and first version of our action library \cite{aein2013toward}.
\begin{figure*}
      \centering
      \includegraphics[scale=0.20]{./pdf/action_graph_sec.pdf}
      \caption{ An example of the put-on-top action is performed by a human. 
The snapshots of the executed actions together with segmented images are shown (top).
The symbolic graph sequence (middle) and the SEC matrix (bottom) together with 
the required primitives (bottom right) give a high-level definition of the action.
The abstract objects, manipulator, primary object, secondary object and background are the hand, the bucket, the box and the table, respectively.}
      \label{fig:action_graph_sec}
\end{figure*}

\subsection{Ontology of Actions}
\label{sec:ontology}
The \textit{ontology of manipulation actions} \cite{TAMD13} defines human-like manipulation actions in an abstract way.
An action is defined as change of touching relations between pairs of objects.
The hypothesis is that the most important information are encoded in touching relation of objects.
An example put-on-top actions which is performed by human is shown in fig.\ref{fig:action_graph_sec}.
The segmented images and the extracted graph sequence are also shown.
The nodes of the graphs represent objects and presence of an edge indicates that a pair of objects are touching.
The full action is thus summarized by this sequence of graphs.

There are some constraints on the actions defined in this ontology, which are stated as the following rules:
\begin{itemize}
 \item \textbf{Rule 1:} The action must cause some change in the touching relation of objects, including the manipulator (human or robot hand)
 \item \textbf{Rule 2:} The action is performed by one hand. This is true for the most of human actions, since the second hand is usually used as support.
 \item \textbf{Rule 3:} The hand is free at the beginning and at the end of action.
 \item \textbf{Rule 4:} The hand touches one object at the beginning of action and does not purposefully touch another object in the scene.
\end{itemize}

@@

\subsection{Abstract objects}

There are too many objects in the real world.
It is not practical to define each action separately for each object.
It is then necessary to define manipulation actions in a general way so that they are applicable to different objects.
To deal with this problem, we define objects by the role that they play in the action.
First of all, one object is needed that performs the action, which is here called the \textit{manipulator}.
Then, there exists an object that is manipulated directly by the manipulator.
This object is called \textit{primary object}.
For example, in the put-on-top action in fig.\ref{fig:action_graph_sec}, the human hand is the manipulator and the bucket is the primary object.

In some actions there is another object which is indirectly manipulated by the manipulator.
For example if the hand picks up a bucket and puts it on a box, as shown in fig.\ref{fig:action_graph_sec},
the box plays the role of the indirect object or the \textit{secondary object}.
There could be more than one indirect objects in an action, but in this work we will consider actions with one indirect object.

Adding the relation of objects with the background is important in representing and executing the actions (See \cite{TAMD13}).
By adding the background, different graphes emerge for ``one object on top of another object'' and ``one object next to another object''.
Another advantage of adding the background is that it adds an ``air-phase'' to actions,
which happens when one object is lifted and moving on air, but it is not yet touching the other object.

@@

\begin{table}
\caption{Abstract relations and their attributes for the put-on-top action}
\begin{tabular}{ lllll }
\hline\noalign{\smallskip}
Relation Name & Abstract Relation & Real Relation & Type \\
\noalign{\smallskip}\hline\noalign{\smallskip}
$\text{R}_1$  & R(manipulator,primary object) & R(hand,bucket) & variable \\
$\text{R}_2$  & R(manipulator,secondary object)& R(hand,box) & don't-care \\
$\text{R}_3$  & R(manipulator,background) & R(hand,table) & don't-care \\
$\text{R}_4$  & R(primary object,secondary object) & R(bucket,box) & variable  \\
$\text{R}_5$  & R(primary object,background) & R(bucket,table) & variable \\
$\text{R}_6$  & R(secondary object,background)& R(box,table) & constant \\
\noalign{\smallskip}\hline
\end{tabular}
\label{tab:relations}
\end{table}

\subsection{Abstract relations}
The relations between objects play the key role in the definition of the actions.
These abstract relations are assigned to pairs of abstract objects (See Table \ref{tab:relations}).
If there exists $N$ objects in an action,
there will be $N(N-1)/2$ distinct relations.
As stated before, there are 4 abstract objects in our defintion, which gives in total 6 abstract relations.

Each relation is defined by two attributes, which are  \emph{type} and \emph{value}.
The \emph{type} of a relation is determined by the importance and variation of that relation throughout the action.
For example for the put-on-top action, the relation between the hand and the table, does not affect the outcome of the action.
The type of such relations is \emph{don't-care}.
The importance of a relation is decided based on common sense.

Other relations, which are important for an action, are divided into \emph{variable} and \emph{constant} relations.
For example, the relation between manipulator(hand) and primary object(bucket) for the put-on-top action is \emph{variable},
whereas the relation between the secondary object(box) and the background(table) is \emph{constant} (see Fig. \ref{fig:action_graph_sec}).
The constant relations show the necessary conditions to perform an action and a change in them implies failure of the action.
On the other hand, variable relations encode the progress of the action and play the most important role in our methodology.

@@

\subsection{Semantic Event Chain}
\label{sec:SEC}
The actions in the ontology are defined as sequences of graphs (see Fig.\ref{fig:action_graph_sec}).
The nodes of these graphs are the objects and the edges show the touching relation between a pair of objects.
A semantic event chain (SEC) \cite{Aksoy11} is a matrix derived from these graph sequences.
Each row of the SEC matrix shows changes that occur in one abstract relation.
Since there are six abstract relations, the SEC matrix has 6 rows.
The number of columns of SEC, depends on how many times the relations between objects change in the course of action.
Each column of SEC matrix is interpreted as a state of the scene, which is a combination of the relations between the objects.

The valid symbolic entries of SEC matrix are N (not touching), T (touching) and A ( absence).
In a SEC, the progress of the action from the beginning to the end, is seen in a compact way.
In addition, the SEC matrix of different instances of one action remains the same.
The SEC matrix of the put-on-top action is shown in Fig.\ref{fig:action_graph_sec}.

\subsection{Abstract Primitives}
\label{sec:abstract_primitives}
In the simple example at the beginning of this section, it is shown that a full action can be divided into several sub-actions.
These sub-actions or \textit{primitives} are the basic functions of the manipulator.

@@

\subsection{Abstract Positions}

As described above, one important primitive is the $move(pose)$ primitive that moves the robot arm toward a pose.
In the abstract definition, the argument $pose$ of this primitive is an abstract position.
The abstract positions are either the objects in the scene, or some other convenient points in space.
While performing the actions, sometimes we move our hands toward points in space where there are no specific objects.
One example is when we initially lift an object from a table, to put it on top of another object.
We move the object to a point that makes our next move easier.
We call such positions \textit{home}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% SECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Low-level Action Definition}
\label{sec:low-level}
In this section, the abstract components of the high-level definition are related to their real-world counterparts.
This includes defining objects in the real world, implementing the low-level primitives such that proper commands are sent to the hardware control systems,
and calculating the object relations from the sensor data.
In the rest of this section, these steps are described in more detail.

\subsection{Real objects}
In the real world experiments, the abstract objects (\textit{manipulator}, \textit{primary object}, \textit{secondary object} and \textit{background})
are instantiated by real objects in the scene.
For the put-on-top example depicted in Fig. \ref{fig:action_graph_sec},
these objects are manipulator=hand, primary object=bucket, secondary object=box and background=table.
We need to represent the real-world objects in signal space so that we can perform the primitives.

In our work, two pieces of information is needed to represent an object.
First, the position of each object with respect to some fixed frame is needed.
The frame is fixed to the workspace of the robot.
To associate a position to the object, the objects are modeled with a single point, located at their center of mass.
Second, the direction of objects in the XY-plane should be detected.
This is necessary for grasping the objects, as well as some actions like cutting.
Note that we use this direction information only for elongated objects (such as cucumber) but not for symmetric objects (such as apple, cup etc.)
The direction is defined as the angle that the main axis of the object makes with respect to the X-axis of the reference frame.

@@

\begin{table}
\caption{Summary of object relation detection in different actions. For each relation only the main sensor is mentioned.}
\begin{tabular}{ lcccccc }
\hline\noalign{\smallskip}
 Action Name &  $\text{R}_1$ & $\text{R}_2$ &$\text{R}_3$ &$\text{R}_4$ &$\text{R}_5$&$\text{R}_6$ \\
\noalign{\smallskip}\hline\noalign{\smallskip}
 Pick and Place & tactile & -       & position & -     &  force & - \\
 Put-on-top     & tactile & tactile & position & force &  vision & vision \\
 Take-down      & tactile & tactile & position & vision&  force & vision \\
 Put-in         & tactile & tactile & position & force &  vision & vision \\
 Cut            & tactile & tactile & position & force &  position & vision \\
 Unload         & tactile & tactile & position & vision&  force & vision \\
 Stir           & tactile & -       & position & vision&  vision & - \\
 Push           & force   & -       & position & -     &  vision & - \\
 Poke           & force   & -       & position & -     &  vision & - \\
\noalign{\smallskip}\hline
\end{tabular}
\label{tab:relation_detection}
\end{table}
\subsection{Real relations}
\label{sec:real_relations}
The real relations are the actual relations between pairs of objects.
These relations together form a symbolic representation of the scene, or in other words, the current state of system.
To detect the relations, we use combination of vision, position, force and tactile sensors.

@@

The relation of the manipulator with the primary and secondary objects are calculated from the position and tactile sensors.
When the position of the manipulator is close to the \textit{primary} (\textit{secondary}) object and the tactile sensors sense that the manipulator has grasped something,
$\text{R}_1$ ($\text{R}_2$), is changed to T.
Although we can detect the $\text{R}_2$, usually this relation is not important and marked as don't-care.
The reason is that the manipulator does not directly interact with the secondary object.

@@

\subsection{Low-level primitives}
\label{section_primitives}
In section.\ref{sec:abstract_primitives} we defined the primitives which are performed by the manipulator.
Here we describe our implementation of these primitives at the low-level.

>>>>

%\title{Library of Actions: Implementing Human-like Manipulation Actions based on Semantic Event Chains}
\title{Library of Actions: Implementing a Generic Robot Execution Framework by Using Manipulation Action Semantics}

@@

In this paper a new implementation of the library of actions is presented.
Library of actions is a software application which implements  manipulation actions on robotic systems by using the semantic event chain framework.
A general definition for manipulation actions is presented which contains both in symbolic and sub-symbolic components.
To link these two domains, a finite state machine is presented for the  execution of manipulation actions.
The actions are performed both individually and chained sequentially to perform more complex scenarios.
This opens the possibility to use higher-level planners that work in symbolic domain.
The results show that the proposed methodology and software are capable of performing useful human-like actions.

@@

The rest of the paper is organized as follows. We start with introducing the state of the art in  section~\ref{sec:soa}. We then continue with a detailed description of each processing step in  section~\ref{sec:method}. 
Next, section~\ref{sec:Implementing} presents the implementation of actions in the library.
The results of various experiments are shown in section~\ref{sec:results} followed by a discussion in  section~\ref{sec:discussion}.

XXX in the introduciton, mention that we use manipulation actions not in the same context as actions representing whole body movements. However, those terms will be used interchangeably.

XXX mention that perception and action are intertwined, This is supported by the present of mirror neurons. In this sense, SEs are used both phases, therefore, this is the first attempt that shows the same generic action descriptor can be employed for both action perception (encoding) and execution in robots.

XXX SECs is also used as mid-level planners which defines symbolic states. Therefore, we have not introduced any high level planner. (like metta's ICRA paper!)

\begin{figure}[hb]
      \centering
      \includegraphics[scale=0.5]{./pdf/Figure_PerceptionAction.pdf}
      \caption{ Perception-action Chain}
      \label{fig:action_graph_sec}
\end{figure}

%\newpage  %% needed for single columns
\clearpage  %% needed for two columns
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{State of the Art}
\label{sec:soa}

There exists a large corpus of work in action representation and execution \cite{Ijspeert2002,Ude93,Lee2006,Calinon2007}. Two distinct approaches are commonly preferred in order to represent and execute actions, one at the trajectory level \cite{Ijspeert2002} or the other at the symbolic level \cite{Dillmann2010}.
The former gives more flexibility for the definition of actions, while the latter defines actions at a higher level and allows for generalization and planning.

For trajectory level representation there are several well established techniques: splines \cite{Ude93}, Hidden Markov Models \cite{Lee2006}, Gaussian Mixture Models \cite{Calinon2007}, Dynamic Movement Primitives  \cite{Ijspeert2002,Luksch12}.
With trajectory level encoding, one investigates or learns different complicated trajectories, but it is difficult to use them in a ``more cognitive sense''. Generalization of the observed trajectories is the main {\it breaking~point} here, since even the same action can be demonstrated by following various trajectories.

High-level symbolic representations many times use graph structures and relational representations,
e.g., \cite{Pardowitz2007,Ekvall2006,Aksoy2011}. Alternative methods, such as in \cite{Lee2013}, describe a syntactic approach for learning robot imitation by capturing  underlying task structures in the form of probabilistic activity grammars. 
These approaches give compact descriptions of complex tasks,
but they do not consider execution-relevant motion parameter (trajectories, poses, forces) in great detail.
In this work, our high-level action descriptor is based on the concept of Semantic Event Chains (SECs) introduced in  \cite{Aksoy2011}. 
SECs are generic action descriptors that capture the underlying spatiotemporal structure of continuous actions by sampling only
decisive key temporal points derived from the spatial interactions between hands and objects in the scene. The
SEC representation is invariant to large variations in trajectory, velocity, object type and pose used in the action. 
Therefore, SECs can be employed for the classification task of actions as demonstrated in various experiments in  \cite{Aksoy2010,Aksoy2011,Aksoy2011b,Aksoy2013,AksoyRAS2014}. 
In contrast to works in  \cite{Pardowitz2007,Ekvall2006}, we have already shown in \cite{Aksoy2011b} that actions encoded by SEC can be executed once the low-level data (object positions, trajectories etc.) are provided.

The concept of semantic event chains has also  been successfully utilized and extended by others \cite{Waechter2013,Luo2011,Vuga2014,David2014} for monitoring or execution purposes. The work in \cite{Waechter2013} addressed the reproduction of the obtained human action sequence by parameterizing semantic conclusive sub-actions with the SEC framework.
Active learning of goal directed manipulation sequences, each was recognized using semantic similarities between event chains, was presented in \cite{David2014}. Scene graphs used in SECs were also represented with kernels in \cite{Luo2011} to further apply different machine learning approaches. Additional trajectory information was used in \cite{Vuga2014} to reduce noisy events occur in SECs. All these studies confirm the scalability of the event chains to various monitoring tasks.

Many times trajectory-level descriptions of actions, object properties and high-level goals of the manipulation are brought together through STRIPS-like planning \cite{Dillmann2010}, resulting in operational although not very transparent systems. The approach in \cite{Ahmadzadeh2015} attempts to integrate symbolic action 
representation and planner with motor skill learner. The robot learns the goal of the human demonstrated actions by using
the Visuospatial Skill Learning (VSL) method which produces symbolic predicates. Such predicates are directly fed to a standard planner to encode skills in a discrete symbolic form. The proposed framework also considers the sensorimotor skills, such as the followed trajectory information from
the observed action. However, such approaches are not evaluated on long and complex human manipulation actions. 
Thus, how to bring these two levels together remains a big challenge for robotics.

\red{SoA section needs to be extended to, at least, one page!...}

\clearpage  %% needed for two columns

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{High-level Action Definition}
\label{sec:high-level}

In this section we give a high-level definition of manipulation actions.
At this level, definitions are mainly symbolic, abstract and close to human description.

A simple action like putting a bucket on a box may be described by a human as following:
\begin{enumerate}
  \item \textbf{\textit{Approach}} the bucket
  \item \textbf{\textit{Grasp}} the bucket
  \item \textbf{\textit{Put}} the bucket on the box
  \item \textbf{\textit{Release}} the bucket
\end{enumerate}
This description is by no means unique.
One could easily describe the same action in different words, with different number of steps and different details.
However, one could still extract some common and descriptive properties from this simple description:
\begin{itemize}
  \item \textbf{Property 1:} The definition is still valid even if the objects are altered.
  \item \textbf{Property 2:} An action can be broken into a sequence of smaller primitives such as \textit{approach} and \textit{grasp}.
  \item \textbf{Property 3:} There are conditions to end one primitive and start the next. In the above example these conditions are rather implicit.
  \item \textbf{Property 4:} As humans, we roughly know how to perform these primitives.
  Although our exact movements are produced when we see the objects and perform the action.
\end{itemize}

Our approach to execute human-like actions with robots is similar to this simple example.
We will define a high-level definition of actions which will be independent from the manipulated objects in the action (Property 1),
and consists of a sequence of primitives (Property 2).
The conditions to start and end each primitive are defined explicitly (Property 3).
We will store the default trajectory parameters to execute actions in the high-level definition.
When the real objects are seen at each specific instance of the action, these parameters are used to generate the movements (Property 4).

This high-level symbolic definition has several components which will be described in the rest of this section.
For the put-on-top example, the resulting components are shown in fig.\ref{fig:action_graph_sec}.
This definition is an extension to our previous works on the ontology of actions \cite{TAMD13}, semantic event chains (SEC) \cite{Aksoy2011b},
and first version of our action library \cite{aein2013toward}.
\begin{figure*}
      \centering
      \includegraphics[scale=0.20]{./pdf/action_graph_sec.pdf}
      \caption{ An example of the put-on-top action is performed by a human. 
The snapshots of the executed actions together with segmented images are shown (top).
The symbolic graph sequence (middle) and the SEC matrix (bottom) together with 
the required primitives (bottom right) give a high-level definition of the action.
The abstract objects, manipulator, primary object, secondary object and background are the hand, the bucket, the box and the table, respectively.}
      \label{fig:action_graph_sec}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Ontology of Actions}
\label{sec:ontology}

The \textit{ontology of manipulation actions} \cite{TAMD13} defines human-like manipulation actions in an abstract way.
An action is defined as change of touching relations between pairs of objects.
The hypothesis is that the most important information are encoded in touching relation of objects.
An example put-on-top actions which is performed by human is shown in fig.\ref{fig:action_graph_sec}.
The segmented images and the extracted graph sequence are also shown.
The nodes of the graphs represent objects and presence of an edge indicates that a pair of objects are touching.
The full action is thus summarized by this sequence of graphs.

There are some constraints on the actions defined in this ontology, which are stated as the following rules:
\begin{itemize}
 \item \textbf{Rule 1:} The action must yield some change in the touching relation of objects, including the manipulator (human or robot hand)
 \item \textbf{Rule 2:} The action is performed by one hand. This is true for the most of human actions, since the second hand is usually used as support.
 \item \textbf{Rule 3:} The hand is free at the beginning and at the end of action.
 \item \textbf{Rule 4:} The hand touches one object at the beginning of action and does not purposefully touch another object in the scene.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Abstract objects}

There are too many objects in the real world.
It is not practical to define each action separately for each object.
It is then necessary to define manipulation actions in a general way so that they are applicable to different objects.
To deal with this problem, we define objects by the role that they play in the action.
First of all, one actor is needed that performs the action, which is here called the \textit{manipulator}.
Then, there exists an object that is manipulated directly by the manipulator.
This object is called \textit{primary object}.
For example, in the put-on-top action in fig.\ref{fig:action_graph_sec}, the human hand is the manipulator and the bucket is the primary object.

In some actions there is another object which is indirectly manipulated by the manipulator.
For example if the hand picks up a bucket and puts it on a box, as shown in fig.\ref{fig:action_graph_sec},
the box plays the role of the indirect object or the \textit{secondary object}.
There could be multiple secondary objects in an action as will be shown in the chained actions in section xxx.

Adding the relation of objects with the background is important in representing and executing the actions (See \cite{TAMD13}).
By adding the background, different graphes emerge for ``one object on top of another object'' and ``one object next to another object''.
Another advantage of adding the background is that it adds an ``air-phase'' to actions,
which happens when one object is lifted and moving in the air, but it is not yet touching the other object.

@@

\begin{table*}
\centering
\caption{Abstract relations and their attributes for the put-on-top action}
\begin{tabular}{ lllll }
\hline\noalign{\smallskip}
Relation Name & Abstract Relation & Real Relation & Type \\
\noalign{\smallskip}\hline\noalign{\smallskip}
$\text{R}_1$  & R(manipulator,primary object) & R(hand,bucket) & variable \\
$\text{R}_2$  & R(manipulator,secondary object)& R(hand,box) & don't-care \\
$\text{R}_3$  & R(manipulator,background) & R(hand,table) & don't-care \\
$\text{R}_4$  & R(primary object,secondary object) & R(bucket,box) & variable  \\
$\text{R}_5$  & R(primary object,background) & R(bucket,table) & variable \\
$\text{R}_6$  & R(secondary object,background)& R(box,table) & constant \\
\noalign{\smallskip}\hline
\end{tabular}
\label{tab:relations}
\end{table*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Abstract relations}

The relations between objects play the key role in the definition of the actions.
These abstract relations are assigned to pairs of abstract objects (See Table \ref{tab:relations}).
If there exists $N$ objects in an action,
there will be $N(N-1)/2$ distinct relations.
As stated before, there are 4 abstract objects in our defintion, which gives in total 6 abstract relations.

Each relation is defined by two attributes, which are  \emph{type} and \emph{value}.
The \emph{type} of a relation is determined by the importance and variation of that relation throughout the action.
For example for the put-on-top action, the relation between the hand and the table, does not affect the outcome of the action.
The type of such relations is \emph{don't-care}.
Although the importance of some relations is decided based on common sense, many of them were learned during the observation phase.

Other relations, which are important for an action, are divided into \emph{variable} and \emph{constant} relations.
For example, the relation between manipulator(hand) and primary object(bucket) for the put-on-top action is \emph{variable},
whereas the relation between the secondary object(box) and the background(table) is \emph{constant} (see Fig. \ref{fig:action_graph_sec}).
The constant relations show the necessary pre-conditions to perform an action and a change in them implies failure of the action.
On the other hand, variable relations encode the progress of the action and play the most important role in our methodology.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Semantic Event Chain (SEC)}
\label{sec:SEC}

The actions in the ontology are defined as sequences of graphs (see Fig.\ref{fig:action_graph_sec}).
The nodes of these graphs are the objects and the edges show the touching relation between a pair of objects.
A semantic event chain (SEC) \cite{Aksoy2011} is a matrix derived from these graph sequences.
Each row of the SEC matrix shows changes that occur in one abstract relation.
Since there are six abstract relations, the SEC matrix has 6 rows.
The number of columns of SEC, depends on how many times the relations between objects change in the course of action.
Each column of SEC matrix is interpreted as a state of the scene, which is a combination of the relations between the objects.

The valid symbolic entries of SEC matrix are N (Not touching), T (Touching) and A (Absence).
In a SEC, the progress of the action from the beginning to the end, is seen in a compact way.
In addition, the SEC matrix of different instances of one action remains the same.
The SEC matrix of the put-on-top action is shown in Fig.\ref{fig:action_graph_sec}.

xxx here mention that SECs have always 6 rows but columns can alter in size.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Abstract Primitives}
\label{sec:abstract_primitives}
In the simple example at the beginning of this section, it is shown that a full action can be divided into several primitives.
These primitives or \textit{primitives} are the basic functions of the manipulator.

@@

xxx here, each state transition from one column (state) to the next defines one unique primitive.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Abstract Positions}

As described above, one important primitive is the $move(pose)$ primitive that moves the robot arm toward a pose.
In the abstract definition, the argument $pose$ of this primitive is an abstract position.
The abstract positions are either the objects in the scene, or some other convenient points in space.
While performing the actions, sometimes we move our hands toward points in space where exist no specific objects.
One example is when we initially lift an object from a table, to put it on top of another object.
We move the object to a point that makes our next move easier.
We call such positions \textit{home}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Low-level Action Definition}
\label{sec:low-level}
In this section, the abstract components of the high-level definition are related to their real-world counterparts.
This includes defining objects in the real world, implementing the low-level primitives such that proper commands are sent to the hardware control systems,
and calculating the object relations from the sensor data.
In the rest of this section, these steps are described in more detail.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Real objects}
In the real world experiments, the abstract objects (\textit{manipulator}, \textit{primary object}, \textit{secondary object} and \textit{background})
are instantiated by real objects in the scene.
For the put-on-top example depicted in Fig. \ref{fig:action_graph_sec},
these objects are manipulator=hand, primary object=bucket, secondary object=box and background=table.
We need to represent the real-world objects in the signal space so that we can perform the primitives.

In our work, two pieces of information is needed to represent an object.
First, the position of each object with respect to some fixed frame is needed.
Note that the frame is fixed to the workspace of the robot.
To associate a position to the object, the objects are modeled with a single point, located at their center of mass.
Second, the direction of objects in the XY-plane should be detected.
This is necessary for grasping the objects, as well as some actions like cutting.
Note that we use this direction information only for elongated objects (such as cucumber) but not for symmetric objects (such as apple, cup etc.)
The direction is defined as the angle that the main axis of the object makes with respect to the X-axis of the reference frame.

@@

\begin{table*}
\centering
\caption{Summary of object relation detection in different actions. For each relation only the main sensor is mentioned.}
\begin{tabular}{ lcccccc }
\hline\noalign{\smallskip}
 Action Name &  $\text{R}_1$ & $\text{R}_2$ &$\text{R}_3$ &$\text{R}_4$ &$\text{R}_5$&$\text{R}_6$ \\
\noalign{\smallskip}\hline\noalign{\smallskip}
 Pick and Place & tactile & -       & position & -     &  force & - \\
 Put-on-top     & tactile & tactile & position & force &  vision & vision \\
 Take-down      & tactile & tactile & position & vision&  force & vision \\
 Put-in         & tactile & tactile & position & force &  vision & vision \\
 Cut            & tactile & tactile & position & force &  position & vision \\
 Unload         & tactile & tactile & position & vision&  force & vision \\
 Stir           & tactile & -       & position & vision&  vision & - \\
 Push           & force   & -       & position & -     &  vision & - \\
 Poke           & force   & -       & position & -     &  vision & - \\
\noalign{\smallskip}\hline
\end{tabular}
\label{tab:relation_detection}
\end{table*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Real relations}
\label{sec:real_relations}
The real relations are the actual relations between pairs of objects.
These relations together form a symbolic representation of the scene, or in other words, the current state of system.
To detect the relations, we use combination of vision, position, force and tactile sensors.

@@

The relation of the manipulator with the primary and secondary objects are calculated from the position and tactile sensors.
When the position of the manipulator is close to the \textit{primary} (\textit{secondary}) object and the tactile sensors sense that the manipulator has grasped something,
$\text{R}_1$ ($\text{R}_2$), is switched to T.
Although we can detect the $\text{R}_2$, usually this relation is not important and marked as don't-care.
The reason is that the manipulator does not directly interact with the secondary object.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Low-level primitives}
\label{section_primitives}
In section.\ref{sec:abstract_primitives} we defined the primitives which are performed by the manipulator.
Here we describe our implementation of these primitives at the low-level.
